### 2024-02-18 paper_sisc_first_revision/localpsf.tex
Allow the user to vary the RBF shape parameter, rather than having it as a hardcoded constant

The shape parameter $\epsilon$ mediates a tradeoff between accuracy and stability. Small $\epsilon$ is required for RBF interpolation with Gaussian kernels to achieve high accuracy, but small $\epsilon$ also makes RBF interpolation less robust to errors or nonsmoothness in the function being interpolated. 
%This is illustrated in Figure \ref{fig:RBF_width} for a simple one dimensional interpolation problem. 
If high accuracy is not required (for example, if the method is being used to construct a preconditioner) we recommend a conservative choice of $\epsilon=3.0$ in order to make the method more robust to nonsmoothness of the kernel, discretization error, violations of our assumptions, and issues related to boundaries. We use $\epsilon=3.0$ in our numerical results involving Hessians for this reason. In our numerical results for blur kernels, we use a smaller value of $\epsilon=0.5$ so that the RBF interpolation accuracy is not a limiting factor as we study convergence of the method.

>>>>

The shape parameter, $\epsilon$, mediates a tradeoff between accuracy and stability. Small $\epsilon$ is required for RBF interpolation with Gaussian kernels to achieve high accuracy, but small $\epsilon$ also makes RBF interpolation less robust to errors or nonsmoothness in the function being interpolated. 
%This is illustrated in Figure \ref{fig:RBF_width} for a simple one dimensional interpolation problem. 
If high accuracy is not required (for example, if the method is being used to construct a preconditioner) we recommend a conservative choice of $\epsilon=3.0$ in order to make the method more robust to nonsmoothness of the kernel, discretization error, errors caused by violations of our assumptions, and issues related to boundaries. We use $\epsilon=3.0$ in our numerical results involving Hessians for this reason. In our numerical results for blur kernels, we use a smaller value of $\epsilon=0.5$ so that the RBF interpolation accuracy is not a limiting factor as we study convergence of the method.
